Tutorial_2

### 2024-07-24 Tutorial_2_Bayesian/Tutorial_2.Rmd
update Tutorial 2

```{r load-data}
ptb_data <- read_csv("Tutorial_1_descriptive_stats/data/inputfile_hazard_modeling.csv")
print(ptb_data,n=30)
summary(ptb_data) # 26602 rows: 6 participants, 3 conditions, 15 periods, and event indicator (0/1)
```

@@

# create dummy variables for each time period (to illustrate how to fit a general specification of TIME)
ptb_data <- ptb_data %>% mutate(d6 = if_else(period == 6, 1, 0),
                                d7 = if_else(period == 7, 1, 0),
                                d8 = if_else(period == 8, 1, 0),
                                d9 = if_else(period == 9, 1, 0),
                                d10 = if_else(period == 10, 1, 0),
                                d11 = if_else(period == 11, 1, 0),
                                d12 = if_else(period == 12, 1, 0),
                                d13 = if_else(period == 13, 1, 0),
                                d14 = if_else(period == 14, 1, 0),
                                d15 = if_else(period == 15, 1, 0))

# remove unnecessary columns before fitting a model
ptb_data <- ptb_data %>% select(-c(bl,tr,trial,period,d6,d7,d8,d9,d10,d11,d12,d13,d14,d15)) # 12840 obs. of 5 variables
head(ptb_data,n=17)
summary(ptb_data)
```

>>>>

```{r load-data}
ptb_data <- read_csv("Tutorial_1_descriptive_stats/data/inputfile_hazard_modeling.csv")
print(ptb_data,n=30)
summary(ptb_data) # 26602 rows: 6 participants, trial, 3 conditions, 15 periods, and event indicator (0/1)
```

@@

# remove unnecessary columns before fitting a model
ptb_data <- ptb_data %>% select(-c(bl,tr,trial,period)) # 12840 obs. of 5 variables
head(ptb_data,n=17)
summary(ptb_data)
# 6 subjects
# condition: blank (6401), congruent (2642), incongruent (3797)
# period_9: -3 to 6
# trial_c: -0.999 to 0.540
```
